On the uniqueness and stability of dictionaries \\ for sparse representation of noisy signals

### 2019-05-10 manuscripts/IEEE/final_submission.tex
is and js

\begin{definition}\label{sip}
Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $\sigma(i)$ is the collection of sets in $\mathcal{H}$ containing $i$. We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \sigma(j) = \{i\}$ for all $i \in [m]$. 
\end{definition}

@@

Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying $L_2(\mathbf{A}) > 0$, since here we have $2\mathcal{H} = {[m] \choose 2}$, and suppose some $\mathbf{B}$ and $1$-sparse $\mathbf{\overline x}_i \in \mathbb{R}^{\overline m}$ have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$. Then, there exist $\overline{c}_1, \ldots, \overline{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\overline m]$ such that:
\begin{align}\label{1D}
\|c_j\mathbf{A}_j - \overline{c}_j\mathbf{B}_{\pi(j)}\|_2 \leq \varepsilon,\ \ \text{for $j \in [m]$}.
\end{align} 
Note that $\overline{c}_j \neq 0$, since otherwise we would reach the following contradiction: $\|\mathbf{A}_j \|_2 \leq C_1 |c_j| \|\mathbf{A}_j \|_2  \leq C_1\varepsilon < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{j \in [m]} \|\mathbf{A}_{j}\|_2$. %implies by \eqref{delrho} the contradiction $|c_j| < \min_{\ell \in [m]} | c_\ell |$.

We now show that $\pi$ is injective (in particular, a permutation if $\overline m = m$). Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$. Then, $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$ and $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$, and we have: %Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality to annihilate the terms in $\mathbf{B}_\ell$, we obtain:
\begin{align*}
(|\overline{c}_{i}| + |\overline{c}_{j}|) \varepsilon
&\geq |\overline{c}_{i}| \|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2  + |\overline{c}_{j}| \|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2 \nonumber \\
&\geq \|\mathbf{A}(\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
&\geq  L_2(\mathbf{A}) \|\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i}\|_2 \nonumber \\
&\geq  L_2(\mathbf{A}) \left( |\overline{c}_{i}| + |\overline{c}_{j}| \right) \min_{\ell \in [m]} |c_\ell |,
\end{align*}
contradicting our assumed upper bound on $\varepsilon$. Hence, the map $\pi$ is injective and so $\overline m \geq m$. %Setting $\overline J = \pi([m])$ and

Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(j)}$ and $\frac{\overline{c}_j}{c_j}\mathbf{e}_j$ for $j \in [m]$ (otherwise, $\mathbf{e}_{j}$ for $j \in [\overline{m}] \setminus [m]$), we may rewrite \eqref{1D} to see that for all $j \in [m]$:
\begin{align*}
\|\mathbf{A}_j - (\mathbf{BPD})_j\|_2 
= \|\mathbf{A}_j - \frac{\overline{c}_j}{c_j}\mathbf{B}_{\pi(j)}\|_2 
\leq \frac{\varepsilon}{|c_j|} 
\leq C_1\varepsilon.
\end{align*}
%\vspace{-.2 cm}
\end{proof}

@@

If for some $n \times \overline m$ matrix $\mathbf{B}$ and map $\pi: \mathcal{H} \mapsto {[\overline m] \choose k}$,
\begin{align}\label{GapUpperBound}
d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \  \text{for $S \in \mathcal{H}$},
\end{align}
then $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
\begin{align}\label{MainLemmaBPD}
\|\mathbf{A}_j - (\mathbf{B}\mathbf{PD})_j\|_2 \leq C_2 \varepsilon, \ \  \text{for } j \in J,
\end{align}
for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}.
\end{lemma}

>>>>

\begin{definition}\label{sip}
Given $\mathcal{H} \subseteq 2^{[m]}$, the \textbf{star} $\sigma(i)$ is the collection of sets in $\mathcal{H}$ containing $i$. We say $\mathcal{H}$ has the \textbf{singleton intersection property} (\textbf{SIP}) when $\cap \sigma(i) = \{i\}$ for all $i \in [m]$. 
\end{definition}

@@

Fix $\mathbf{A} \in \mathbb{R}^{n \times m}$ satisfying $L_2(\mathbf{A}) > 0$, since here we have $2\mathcal{H} = {[m] \choose 2}$, and suppose some $\mathbf{B}$ and $1$-sparse $\mathbf{\overline x}_i \in \mathbb{R}^{\overline m}$ have  $\|\mathbf{A}\mathbf{x}_i - \mathbf{B}\mathbf{\overline x}_i\|_2 \leq \varepsilon < L_2(\mathbf{A}) / C_1$ for all $i$. Then, there exist $\overline{c}_1, \ldots, \overline{c}_m \in \mathbb{R}$ and a map $\pi: [m] \to [\overline m]$ such that:
\begin{align}\label{1D}
\|c_i\mathbf{A}_i - \overline{c}_i\mathbf{B}_{\pi(i)}\|_2 \leq \varepsilon,\ \ \text{for $i \in [m]$}.
\end{align} 
Note that $\overline{c}_i \neq 0$, since otherwise we would reach the following contradiction: $\|\mathbf{A}_i \|_2 \leq C_1 |c_i| \|\mathbf{A}_i \|_2  \leq C_1\varepsilon < L_2(\mathbf{A}) \leq L_1(\mathbf{A}) = \min_{i \in [m]} \|\mathbf{A}_{i}\|_2$. %implies by \eqref{delrho} the contradiction $|c_i| < \min_{\ell \in [m]} | c_\ell |$.

We now show that $\pi$ is injective (in particular, a permutation if $\overline m = m$). Suppose that $\pi(i) = \pi(j) = \ell$ for some $i \neq j$ and $\ell$. Then, $\|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2  \leq \varepsilon$ and $\|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2 \leq \varepsilon$, and we have: %Scaling and summing these inequalities by $|\overline{c}_{i}|$ and $|\overline{c}_{j}|$, respectively, and applying the triangle inequality to annihilate the terms in $\mathbf{B}_\ell$, we obtain:
\begin{align*}
(|\overline{c}_{i}| + |\overline{c}_{j}|) \varepsilon
&\geq |\overline{c}_{i}| \|c_{j}\mathbf{A}_{j} - \overline{c}_{j}\mathbf{B}_{\ell}\|_2  + |\overline{c}_{j}| \|c_{i}\mathbf{A}_{i} - \overline{c}_{i} \mathbf{B}_{\ell}\|_2 \nonumber \\
&\geq \|\mathbf{A}(\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i})\|_2 \nonumber \\ 
&\geq \sqrt{2}  L_2(\mathbf{A}) \|\overline{c}_{i}c_{j} \mathbf{e}_{j} - \overline{c}_{j}c_{i}\mathbf{e}_{i}\|_2 \nonumber \\
&\geq  L_2(\mathbf{A}) \left( |\overline{c}_{i}| + |\overline{c}_{j}| \right) \min_{\ell \in [m]} |c_\ell |,
\end{align*}
contradicting our assumed upper bound on $\varepsilon$. Hence, the map $\pi$ is injective and so $\overline m \geq m$. %Setting $\overline J = \pi([m])$ and

Letting $\mathbf{P}$ and $\mathbf{D}$ be the $\overline m \times \overline m$ permutation and invertible diagonal matrices with, respectively, columns $\mathbf{e}_{\pi(i)}$ and $\frac{\overline{c}_i}{c_i}\mathbf{e}_i$ for $i \in [m]$ (otherwise, $\mathbf{e}_{i}$ for $i \in [\overline{m}] \setminus [m]$), we may rewrite \eqref{1D} to see that for all $i \in [m]$:
\begin{align*}
\|\mathbf{A}_i - (\mathbf{BPD})_i\|_2 
= \|\mathbf{A}_i - \frac{\overline{c}_i}{c_i}\mathbf{B}_{\pi(i)}\|_2 
\leq \frac{\varepsilon}{|c_i|} 
\leq C_1\varepsilon.
\end{align*}
%\vspace{-.2 cm}
\end{proof}

@@

If for some $n \times \overline m$ matrix $\mathbf{B}$ and map $\pi: \mathcal{H} \mapsto {[\overline m] \choose k}$,
\begin{align}\label{GapUpperBound}
d(\bm{\mathcal{A}}_S, \bm{\mathcal{B}}_{\pi(S)}) \leq \varepsilon, \ \  \text{for $S \in \mathcal{H}$},
\end{align}
then $\overline m \geq m$, and provided $\overline m (r-1) < mr$, there is a permutation matrix $\mathbf{P}$ and invertible diagonal $\mathbf{D}$ such that:
\begin{align}\label{MainLemmaBPD}
\|\mathbf{A}_i - (\mathbf{B}\mathbf{PD})_i\|_2 \leq C_2 \varepsilon, \ \  \text{for } i \in J,
\end{align}
for some $J \subseteq [m]$ of size \mbox{$m - (r-1)(\overline m - m)$}.
\end{lemma}
